Numerical simulation and entropy dissipative cure of the carbuncle instability for the shallow water circular hydraulic jump

### 2021-01-13 numerics_paper/version2/numerical_chj.tex
Add section on flow past a cylinder.
Also some minor improvements to code.

\subsection{Steady shock around a cylinder}\label{sec:bow_shock}

>>>>

\subsection{Flow past a cylinder}\label{sec:bow_shock}
In this section we consider the formation of a bow shock when a
uniform flow encounters a cylindrical obstacle.  This problem has
been studied previously in the context of carbuncle formation in
several works for the Euler equations and in
\cite{kemm2014note,bader2014carbuncle} for the shallow water equations.
We present results for existing solvers as a form of verification,
along with results for the new blended solver.  The main question of
interest is the formation of carbuncles.  It is known, for instance,
that the Roe solver incorrectly generates a carbuncle at the center
of the bow shock.

We model only the flow on the upstream side of the cylinder, since
our interest is in the resolution of the bow shock.  We take the domain
$[0,40]\times[0,100]$ with a cylinder of radius 20 centered at $(40,50)$.
Reflecting boundary conditions are imposed at the surface of the cylinder,
along with outflow conditions along the rest of the right edge of the domain.
The depth and velocity are set initially and (for all time) at the other
boundaries to $h_0=1$, $u_0=5$, for a Froude number of 5.  We use a $160 \times 400$
uniform Cartesian grid.

We show results at $t=80$, after the flow has reached
a steady state.  With a Roe solver, negative values are generated at an early
time, leading to failure of the solver.  Therefore, we show results only for
HLLE, HLLEMCC, and the blended solver.  These three methods give very similar
results.

\begin{figure}[!h]
  {\scriptsize
    \includegraphics[scale=0.3]{figures/cylinder_HLLE.png}
    \qquad \qquad \qquad
    \includegraphics[scale=0.3]{figures/cylinder_HLLEMCC.png}
    \qquad \qquad \qquad
    \includegraphics[scale=0.3]{figures/cylinder_ES.png}
  }
  \caption{
    Flow past a cylinder.  Results for HLLE, HLLEMCC, and the blended solver.
    \label{fig:steady_outflow}}
\end{figure}

We have also conducted a more challenging version of this test, in which
the velocity within the domain is initially zero.  In that case, the HLLE
and blended solvers give carbuncle-free results similar to Figure \ref{fig:steady_outflow},
but HLLEMCC exhibits a carbuncle.
